From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks

### 2018-05-03 article/article.tex
go_arabidopsis

  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{su2007bacteriome}}
  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.

 \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
  For the Arabidopsis dataset, the complex sources were more limited.
  Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{orchard2013mintact}.
\end{itemize}

>>>>

  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{su2007bacteriome}}
  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
  The network contains 1913 nodes and 7252 edges, the protein complexes range in size between 3 and 65 nodes.
  85\% of the complexes contain 10 or less nodes.

 \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}.
  The network itself contains 4519 nodes and 11096 edges.
  For the Arabidopsis dataset, the complex sources were more limited.
  Consequently, we obtained all gene ontology annotations under the GO term \textit{``Protein-containing complex''} from AmiGO \cite{carbon2009amigo} with the label ``physical interaction evidence used in manual assertion''.
  At the time of writing, this resulted in <INSERT> complexes within the network.

\end{itemize}
